### 2014-05-13 tests/testthat/gp_mcmc_example.Rmd
knit scripts  as tests

---
layout: page
---

```{r plotting-options, message=FALSE, warning=FALSE, include=FALSE}
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE, comment=NA)
library(ggplot2) # plotting 
opts_knit$set(upload.fun = socialR::flickr.url)
theme_set(theme_bw(base_size=10))
theme_update(panel.background = element_rect(fill = "transparent", colour = NA),
             plot.background = element_rect(fill = "transparent", colour = NA))

>>>>

```{r plotting-options, message=FALSE, warning=FALSE, include=FALSE}
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE, comment=NA)
library(ggplot2) # plotting 
#opts_knit$set(upload.fun = imgur_upload)
theme_set(theme_bw(base_size=10))
theme_update(panel.background = element_rect(fill = "transparent", colour = NA),
             plot.background = element_rect(fill = "transparent", colour = NA))
